Instructions for ACL-IJCNLP 2021 Proceedings

### 2021-05-31 reports/SemDial2021/semdial.tex
svg for box swda, few more words

>>>>

% we analyse DAs according to their association with laughter and provide some qualitative insights

\begin{figure}
  \includegraphics[width=\linewidth]{img/box-swda.pdf}
  \caption{SWDA}
  \label{fig:box-swda}
\end{figure}

% 1. overview: rather uniform distribution with few outliers
% 2. let's look at outliers
% 3. consider 5 dimensions of relations

We take into consideration five laughter-related dimensions of an
utterance, and create 5-dimensional representations of dialogue acts
according to them. Each dimension's value equals to the proportion of
utterances of a given type containing laughter.
\begin{enumerate}
\item current utterance;
\item previous utterance by the same speaker;
\item previous utterance by the other speaker;
\item next utterance by the same speaker;
\item next utterance by the other speaker.
\end{enumerate}

For instance,
